---
title: "Statistic"
output: html_document
---

```{r , include=FALSE}
library(plyr)
library(dplyr)
```

```{r load data}
stat <- read.csv('plays_split.csv', header = TRUE, sep=',')
```

Remove empty values
```{r clear}
stat <- subset(stat, !is.na(defendersInTheBox))
stat <- subset(stat, !is.na(numberOfPassRushers))
stat <- subset(stat, offenseFormation != '')
stat <- subset(stat, typeDropback != '')
```

Add additional columns for statistic:
-counts'  for counting;
-success'  factor of success attack, if 'playResult' > 10 then success;
```{r}
stat$counts <- 1
stat$success <- 0
stat$success[stat$playResult >= 10] <- 1
```

Grouping values to find all possible interceptions
```{r group}
groupColumns = c("offenseFormation","typeDropback", "defendersInTheBox", "numberOfPassRushers", "success")
dataCol = c("counts")
#res <- ddply(week_time_qb, groupColumns, function(x) colMeans(x[dataColumns]) )
res <- ddply(stat, groupColumns, function(x) colSums(x[dataCol]))
res <- subset(res, counts > 30)


single_grp_form <- aggregate(res$counts, by=list(offenseFormation=res$offenseFormation), FUN=sum)
single_grp_type <- aggregate(res$counts, by=list(typeDropback=res$typeDropback), FUN=sum)
single_grp_box <- aggregate(res$counts, by=list(defendersInTheBox=res$defendersInTheBox), FUN=sum)
single_grp_rush <- aggregate(res$counts, by=list(numberOfPassRushers=res$numberOfPassRushers), FUN=sum)

grouped_pos <- aggregate(res$counts, by=list(offenseFormation=res$offenseFormation, typeDropback=res$typeDropback), FUN=sum)
grouped_def <- aggregate(res$counts, by=list(defendersInTheBox=res$defendersInTheBox, numberOfPassRushers=res$numberOfPassRushers), FUN=sum)

all_grp <- aggregate(res$counts, by=list(offenseFormation=res$offenseFormation, 
                                         typeDropback=res$typeDropback, 
                                         defendersInTheBox=res$defendersInTheBox, 
                                         numberOfPassRushers=res$numberOfPassRushers), 
                     FUN=sum)
```


All interceptions:
-'countsOfFormation' - number of 'offenseFormation' type;
-'countOfDropback' - number of 'typeDropback' type;
-'countOfDefInBox' - number of 'defendersInTheBox' type;
-'countOfRushers' - number of 'numberOfPassRushers' type;
-'countOfposition' - number of 'offenseFormation + typeDropback' type;
-'countsOfDef' - number of 'defendersInTheBox + numberOfPassRushers' type;
-'totalAll' - number of success (=1) and not success (=0) attacks;

```{r interceptions}
res <- res %>% rowwise %>% do({
  result = as_data_frame(.)
  result$countsOfFormation = single_grp_form[single_grp_form$offenseFormation == result$offenseFormation, 2]
  result$countOfDropback = single_grp_type[single_grp_type$typeDropback == result$typeDropback, 2]
  result$countOfDefInBox = single_grp_box[single_grp_box$defendersInTheBox == result$defendersInTheBox,2]
  result$countOfRushers = single_grp_rush[single_grp_rush$numberOfPassRushers == result$numberOfPassRushers,2]
  
  result$countOfposition = grouped_pos[grouped_pos$offenseFormation == result$offenseFormation & 
                                             grouped_pos$typeDropback == result$typeDropback, 3]
  
  result$countsOfDef = grouped_def[grouped_def$defendersInTheBox == result$defendersInTheBox & 
                                             grouped_def$numberOfPassRushers == result$numberOfPassRushers, 3]
  
  result$totalAll = all_grp[all_grp$offenseFormation == result$offenseFormation & 
                              all_grp$typeDropback == result$typeDropback &
                              all_grp$defendersInTheBox == result$defendersInTheBox & 
                              all_grp$numberOfPassRushers == result$numberOfPassRushers, 5]
  
  result
})
```

Percent - number success or not success attacks of 'totalAll'
```{r}
res <- res %>%
  rowwise %>%
  do({
    result = as_data_frame(.)
    result$Percentage = round ( (result$counts/(result$totalAll))*100 , 2)
    result
  })
```

# Result

```{r result}
res
```
